---
title: "Assignment3_Chunjie_Nan"
author: "Chunjie Nan"
date: "9/12/2021"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"


```{r}
library(stringr)
url<-"https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
major<-read.csv(url)
major<-data.frame(major)
head(major)
str(major)
# There are 174 observations and 3 variables.

data_stat<-grep("DATA|STATISTICS", major$Major, value=F ,ignore.case = TRUE ) 
data_stat
# row 44,52,59 are the majors have data or statistics


major[c(44,52,59),]
```

There are 3 majors contain either DATA or STATISTICS, included "Management Information Systems and Statistics","Computer Programming and Data Processing","Statistics and Decision Science".







### 2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")



```{r}
fruit<-c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
```

```{r}
dput(fruit)
```




The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:
### 3 Describe, in words, what these expressions will match:



(.)\1\1  
The same letters repeats 3times.

"(.)(.)\\2\\1"
two pair letters repeats in symmetrical reverse.

(..)\1
two pair letters repeats twice.

"(.).\\1.\\1"
the same letter repeats 3 times, and separated by any letter.


"(.)(.)(.).*\\3\\2\\1"

three pair letters repeats in symmetrical reverse.





### 4 Construct regular expressions to match words that:
Start and end with the same character.
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)


```{r}
library(stringr)
data("fruit")
data<-data.frame(fruit)
head(fruit)
```
The fruit data from stringr library is used for this problem set.


```{r}
# Start and end with the same character.
str_view(fruit, "^(.).*\1$", match = TRUE)
# it seems no character in the fruit data set has the same letter start and end.
```



```{r}
# Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
str_view(fruit, "(..).*\\1", match = TRUE)
```



```{r}
# Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
str_view(fruit, "(.).*\\1.*\\1", match = TRUE)
```


