---
title: "Week 9 Assignment DATA607 Chunjie Nan"
author: "Chunjie Nan"
date: "10/23/2021"
output: html_document
---

The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.


```{r}
library(httr)
library(jsonlite)

```


From the given website, I chose the "Most Popular API", and the sub-category was most viewed articles. With registration of API, the API-Key is provided as 'ARQt7sTVh2X4fGZidt7OKIMst3UMVzwM'. Finally, I was able to get the json format data set. below url is the website of the data.



### Importing url and convert to a data frame
```{r}
url<-'https://api.nytimes.com/svc/mostpopular/v2/viewed/1.json?api-key=ARQt7sTVh2X4fGZidt7OKIMst3UMVzwM'
get_url <- GET(url, accept_json())
data <- content(get_url, as="text")
data <- fromJSON(data)
popular <- as.data.frame(data)
head(popular)

```



The popular data has 20 observations and 25 variables. There is something new in this popular data that I have never seen before.
under the results.media each variable has 10 sub-variables. I need to find out what is this really meaning.

