---
title: "Week1 Assignment"
author: "Chunjie Nan"
date: "2/2/2020"
output:
  html_document:
    df_print: paged
---
The author of "How Americans Like Their Stake" brings out a question about how does a 
risk-taking behavior associate with steak raness. Along with other variables, he found that
the the risk-taking behavior is statistically insiginificant to steak rareness.
https://fivethirtyeight.com/features/how-americans-like-their-steak/

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(RCurl)
library(plyr)
library(knitr)

```

Import data as csv 

[linked phrase](https://raw.githubusercontent.com/fivethirtyeight/data/master/steak-survey/steak-risk-survey.csv)

```{r import_data}


a<-getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/steak-survey/steak-risk-survey.csv")
b<-data.frame(read.csv(text=a, header=F))
dim(b)
head(b)

```

Rename the column headers
```{r , echo=FALSE}
head(rename(b,c("V1"="ID","V2"="Lottery","V3"="Cigarettes","V4"="Alcohol","V5"="Gamble","V6"="Skydiving", "V7"="Drive_limit", "V8"="Cheat","V9"="Steak","V10"="Steak_prepared","V11"="Gender","V12"="Age","V13"="Income_range", "V14"="Education", "V15"= "Location")))

```


How many female like the steak in rare?
```{r, echo=FALSE}
# How many female like the steak in rare?
steak_rare_female<- subset(b, V11=="Female" & V10 =="Rare")
steak_rare_female
count(steak_rare_female)
```

There are 12 female like the steak rare.

How many male like the steak in rare?
```{r, echo=FALSE}
steak_rare_male<-subset(b, V11 == "Male" & V10 == "Rare")
count(steak_rare_male)


```
There are 10 male like the steak in rare.

```{r}
barplot(table(b$V10),main="Cook Steak")
```

How many steak lovers like the stake in rare?
```{r,echo=FALSE}


steak_lover_rare<- subset(b, V10 == "Rare" & V9 =="Yes")
steak_lover_rare

```
we found that there are 23 steak lovers like eating steak in rare.

Conclusion: The data explains that there are 12 females, and 10 males like the 
steak in rare. Also, we found that people who cook the steak in rere are all steak lovers with total number of 23, and there is a steak lover did not express his or her gender in the data.

