---
title: "Week10_Assignment_Chunjie_Nan"
author: "Chunjie Nan"
date: "10/30/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(dplyr)
library(tidytext)
library(tidyr)
library(janeaustenr)
library(stringr)
library(ggplot2)
library(wordcloud)
library(reshape2)
```



Rererence# 

Silge, J., &amp; Robinson, D. (2017). Text mining with R: A tidy approach. O'Reilly Media. 


## 1. Textbook Code

### 2.2 Sentiment analysis with inner join
```{r}
get_sentiments("afinn")     # value from -5 to 5
get_sentiments("bing")      # negative and positive
get_sentiments("nrc")       # emotions etc

```


```{r}
tidy_books <- austen_books() %>%    #from austen book
  group_by(book) %>%
  mutate(linenumber = row_number(), #setting line number
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%  # detect chapters
  ungroup() %>%
  unnest_tokens(word, text)         #unnest token by word

nrc_joy <- get_sentiments("nrc") %>%#using nrc method
  filter(sentiment == "joy")        #find out the word sentiment equals to joy

tidy_books %>%
  filter(book == "Emma") %>%        #from austen books get the book named Emma
  inner_join(nrc_joy) %>%           #apply the joy sentiment in nrc
  count(word, sort = TRUE) %>%
  head()
```




```{r}
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
#jane_austen_sentiment
```




```{r}
ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")

```



### 2.3 Comparing the three sentiment dictionaries

```{r}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

pride_prejudice%>%
  head()



afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")


bing_and_nrc <- bind_rows(pride_prejudice %>% 
                            inner_join(get_sentiments("bing")) %>%
                            mutate(method = "Bing et al."),
                          pride_prejudice %>% 
                            inner_join(get_sentiments("nrc") %>% 
                                         filter(sentiment %in% c("positive", 
                                                                 "negative"))) %>%
                            mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)


bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")


get_sentiments("nrc") %>% 
     filter(sentiment %in% c("positive", 
                             "negative")) %>% 
  count(sentiment)


get_sentiments("bing") %>% 
  count(sentiment)
```



### 2.4 Most common positive and negative words

```{r}
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts



bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()



custom_stop_words <- bind_rows(tibble(word = c("miss"), 
                                          lexicon = c("custom")), 
                               stop_words)

custom_stop_words
```


### 2.5 Wordclouds

```{r}
tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))


tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)

```



### 2.6 Looking at units beyond just words

```{r}
PandP_sentences <- tibble(text = prideprejudice) %>% 
  unnest_tokens(sentence, text, token = "sentences")
PandP_sentences$sentence[2]



austen_chapters <- austen_books() %>%
  group_by(book) %>%
  unnest_tokens(chapter, text, token = "regex", 
                pattern = "Chapter|CHAPTER [\\dIVXLC]") %>%
  ungroup()

austen_chapters %>% 
  group_by(book) %>% 
  summarise(chapters = n())



bingnegative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

wordcounts <- tidy_books %>%
  group_by(book, chapter) %>%
  summarize(words = n())

tidy_books %>%
  semi_join(bingnegative) %>%
  group_by(book, chapter) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = c("book", "chapter")) %>%
  mutate(ratio = negativewords/words) %>%
  filter(chapter != 0) %>%
  top_n(1) %>%
  ungroup()
```




### My Own Choose from The Harry Potter Book -  Half Blood Price.
Import the first 
```{r}
library(devtools)
install_github("bradleyboehmke/harrypotter")
library(harrypotter)
Title<- c("Half Blood Price")
Book<-list(half_blood_prince)
HBP <- tibble()

for(i in seq_along(Title)) {
        
        clean <- tibble(chapter = seq_along(Book[[i]]),
                        text = Book[[i]]) %>%
             unnest_tokens(word, text) %>%       
             mutate(book = Title[i]) %>%
             select(book, everything())

            HBP<- rbind(HBP, clean)
}

HBP$book <- factor(HBP$book, levels = rev(Title))
head(HBP)
tail(HBP)
```

The Book Half Blood Price has total 30 Chapters. 


### Use Loughran as the new sentiment.

```{r}
HBP %>%
        right_join(get_sentiments("loughran")) %>%
        filter(!is.na(sentiment)) %>%
        count(sentiment, sort = TRUE)

```



### Plot Bing Sentiment


```{r}
HBP %>%
        group_by(book) %>% 
        mutate(word_count = 1:n(),
               index = word_count %/% 500 + 1) %>% 
        inner_join(get_sentiments("bing")) %>%
        count(book, index = index , sentiment) %>%
        ungroup() %>%
        spread(sentiment, n, fill = 0) %>%
        mutate(sentiment = positive - negative,
               book = factor(book, levels = Title)) %>%
        ggplot(aes(index, sentiment, fill = book)) +
          geom_bar(alpha = 0.5, stat = "identity", show.legend = FALSE)

```


### The AFFIN and Loughran

```{r}
AFINN <- HBP %>%
        group_by(book) %>% 
        mutate(word_count = 1:n(),
               index = word_count %/% 500 + 1) %>% 
        inner_join(get_sentiments("afinn")) %>%
        group_by(book, index) %>%
        summarise(sentiment = sum(value)) %>%
        mutate(method = "AFINN")

AFINN
```

```{r}
LOUG <- HBP %>%
            group_by(book) %>% 
            mutate(word_count = 1:n(),
                  index = word_count %/% 500 + 1) %>% 
            inner_join(get_sentiments("loughran")) %>%
            mutate(method = "loughran") %>%
count(book, method, index = index , sentiment) %>%
        ungroup() %>%
        spread(sentiment, n, fill = 0) %>%
        mutate(sentiment = positive - negative) %>%
        select(book, index, method, sentiment)


bind_rows(LOUG, AFINN) %>%
        ungroup() %>%
        mutate(book = factor(book, levels = Title)) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_bar(alpha = 0.7, stat = "identity", show.legend = FALSE) +
  facet_grid(book ~ method)

```




In conclusion, compare the Afinn with Loughran, the AFinn looks more volatile than Loughran method due to most of the loughran sentiment in in between +12.5 and - 12.5. Also, the Analysis tells that loughran distributed more negative sentiment value than the Afinn. It looks Afinn outperformed the loughran in this case. 






